---
title: "Shiny Application for Diamond Price Prediction"
author: "Yuling Tu"
date: "January 27, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


# Goal of the project

- A Shiny application that has widget input, ui input in server.R, reactive output using server calculations, and supporting documentation.

- A Reproducible Pitch Presentation that contains five slides in R Presentation that is pushed to and hosted on GitHub and contains embedded R code that runs.

- All related souce codes are located at Github

### https://github.com/ytu95035/Coursera_DDP

# Diamond Data Set

- Diamond data is from ggplot2 package
- 53940 observations and 10 variables
```{r data, echo=FALSE, comment=NA}
suppressWarnings(suppressPackageStartupMessages(library(ggplot2)))
data("diamonds")
suppressMessages(head(diamonds, 5))
```
- Price & 4c (carat, cut, color and clarity) have positive linear regression relationship
```{r, echo=FALSE, fig.width=16,fig.height=14}
ggplot(diamonds, aes(x=carat, y=price, color=cut)) + geom_point() + facet_grid(color ~ clarity)
```


# Prediction Model

As ggplot shows that 4C has positive linear regression with diamond price.  The following predition model is used to predict the price.

## Model: lm(formula = I(log10(price)) ~ I(carat^(1/3)) + carat + cut + color + clarity, data = diamonds)

The model is contributed by Solomon Messing 

### https://solomonmessing.wordpress.com/2014/01/19/visualization-series-the-scatterplot-or-how-to-use-data-so-you-dont-get-ripped-off/

The application provides the prediction model for you to predict the price by selecting specified 4c you want.

## So, you won't get ripped off EVER!!




